### 2016-10-25 thesis/intro/intro.tex
tmp commit
Started my thesis introduction

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.

@@

@@

@@

@@

\subsection{Obesity associated genetic signatures}
\label{subsec:obesity_associated_genetic_signatures}

\subsubsection{\textbf{\citet{Creighton2012} study}}
\label{ssub:creighton_study}

\subsubsection{\textbf{\citet{Fuentes-Mattei2014} study}}
\label{ssub:fuentes_mattei_study}

\subsection{Pathway associated genetic signatures}
\label{sub:pathway_associated_genetic_signatures}

@@

@@

>>>>

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.
Obesity has been one of the major global problems for more than a decade, associated with many noncommunicable diseases such as diabetes, cardiovascular diseases and certain types of cancers \citep{WHO2014}.
In fact, the risk of comorbidities increases with the increase in \gls{bmi}, where the risk becomes severe as the \gls{bmi} level approaches the obese category.

The number of overweight and obese population, in both adults and children, have risen in every country of the world, and the trend continues as we speak.
Estimated to account for 3.4 million deaths per year and 93.6 million \glspl{daly} in 2010, obesity is a serious disease that continues to grow in our society, which the world cannot ignore (citation from 2010 WHO report needed).

\subsection{Definition of obesity}
\label{sub:definition_of_obesity}
% TODO: add WHO website to the reference for the definition of obesity (or find proper articles)

Obesity is defined as an abnormal or excessive fat accumulation that may impair health of that individual.

One common and widely used approach to categorise individuals is by measuring the \gls{bmi} of the individual.
\gls{bmi} is a measurement based on the weight-to-height ratio of an individual that is used by clinicians and epidemiologists to classify adults into underweight, normal weight, overweight or obese categories.
The unit of \gls{bmi} is defined as the individual's weight in kilograms per square of the height in meters (kg/m$^2$).

\gls{who} (2014) have used \gls{bmi} measurements to define overweight and obesity in adults as an individual with \gls{bmi} $\geq$ 25 kg/m$^2$ and $\geq$ 30 kg/m$^2$, respectively.
For children under the age of 5, overweight and obesity were defined as weight-for-height greater than 2 standard deviation above \gls{who} Child Growth Standards median and greater than 3 standard deviation above the median, respectively.
For children aged between 5 to 19 years, overweight and obesity were defined as BMI-for-age greater than 1 standard deviation above \gls{who} Growth Reference Standards median and greater than 2 standard deviation above the median, respectively.

Although the use of \gls{bmi} as an accurate measure of body fat composition and/or representation of the individual's metabolic status remains controversial, many studies have used \gls{bmi} due to the ease of data collection compared to other measurements, such as [method] (citation needed).
Consequently, most of the publicly available clinical data have height and weight data from which one can calculate the patients' \gls{bmi}, and therefore able to collect the patients' obesity status more conveniently than, for example, waist-to-hip ratio.

@@

% \subsection{Preventive measure of obesity}
% \label{sub:preventive_measure_of_obesity}

@@

\subsection{Impact of obesity}
\label{sub:impact_of_obesity}

@@

\subsection{Microarray technology}
\label{subsec:microarray_technology}

\subsection{Next generation sequencing technology}
\label{sub:next_generation sequencing_technology}

@@

\section{Obesity associated genetic signatures}
\label{sec:obesity_associated_genetic_signatures}

\subsection{\citet{Creighton2012} study}
\label{sub:creighton_study}

\subsection{\citet{Fuentes-Mattei2014} study}
\label{sub:fuentes_mattei_study}

\section{Pathway associated genetic signatures}
\label{sec:pathway_associated_genetic_signatures}

@@

\subsection{\citep{Gatza2011} study}
\label{sub:gatza_study}

@@

This research aims to determine whether gene expression signatures exist  that are specific to obesity across multiple cancer types, and to investigate whether there are any common pathways being dysregulated in cancers based on these genetic signatures.
Better understanding of the pathways being dysregulated in cancer cells in obese patients may lead to improved clinical decisions, and contribute towards personalised treatment in the future.

### 2016-10-25 thesis/misc/glossary.tex
tmp commit
Started my thesis introduction

\newacronym{blca}{BLCA}{bladder urothelial carcinoma}
\newacronym{cesc}{CESC}{cervical squamous cell carcinoma and endocervical adenocarcinoma}
\newacronym{coad}{COAD}{colon adenocarcinoma}
\newacronym{kirp}{KIRP}{kidney renal clear cell carcinoma}
\newacronym{lihc}{LIHC}{liver hepatocellular carcinoma}
\newacronym{read}{READ}{rectum adenocarcinoma}
\newacronym{skcm}{SKCM}{skin cutaneous melanoma}
\newacronym{ucec}{UCEC}{uterine corpus endometrial carcinoma}
\newacronym{geo}{GEO}{Gene Expression Omnibus}
\newacronym{tcga}{TCGA}{The Cancer Genome Atlas}
\newacronym{icgc}{ICGC}{International Cancer Genome Consortium}
\newacronym{bmi}{BMI}{Body Mass Index}
\newacronym{who}{WHO}{World Health Organization}
\newacronym{ln}{LN}{Lymph node}
\newacronym{pr}{PR}{Progesterone receptor}
\newacronym{er}{ER}{Estrogen receptor}
\newacronym{her2}{HER2}{Human epidermal growth factor receptor 2}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{rma}{RMA}{Robust Multi Array}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Glossary terms
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO: make sure you get a proper definitions for all of these glossary terms

\newglossaryentry{rnaseq}{
	name=RNA-seq,
	description={sequence data using transcriptome}
}

\newglossaryentry{r}{
	name=R,
	description={Statistical programming language}
}

\newglossaryentry{metagene}{
	name=Metagene,
	text=metagene,
	description={Summary score of a sample that represents the overall gene expression of the genes that was used to obtain the scores}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Acronym terms
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newacronym{blca}{BLCA}{bladder urothelial carcinoma}
\newacronym{cesc}{CESC}{cervical squamous cell carcinoma and endocervical adenocarcinoma}
\newacronym{coad}{COAD}{colon adenocarcinoma}
\newacronym{kirp}{KIRP}{kidney renal clear cell carcinoma}
\newacronym{lihc}{LIHC}{liver hepatocellular carcinoma}
\newacronym{read}{READ}{rectum adenocarcinoma}
\newacronym{skcm}{SKCM}{skin cutaneous melanoma}
\newacronym{ucec}{UCEC}{uterine corpus endometrial carcinoma}
\newacronym{geo}{GEO}{Gene Expression Omnibus}
\newacronym{tcga}{TCGA}{The Cancer Genome Atlas}
\newacronym{icgc}{ICGC}{International Cancer Genome Consortium}
\newacronym{bmi}{BMI}{Body Mass Index}
\newacronym{who}{WHO}{World Health Organization}
\newacronym{ln}{LN}{Lymph node}
\newacronym{pr}{PR}{Progesterone receptor}
\newacronym{er}{ER}{Estrogen receptor}
\newacronym{her2}{HER2}{Human epidermal growth factor receptor 2}
\newacronym{svd}{SVD}{Singular value decomposition}
\newacronym{rma}{RMA}{Robust Multi Array}
\newacronym{mas}{MAS5}{Microarray Analysis Suite 5.0}
\newacronym{fdr}{FDR}{False Discovery Rate}
\newacronym{go}{GO}{Gene Ontology}
\newacronym[longplural={Disability-Adjusted Life Years}]{daly}{DALY}{Disability-Adjusted Life Year}
